A pipeline to analyse time-course gene expression data

### 2020-07-17 scripts/manuscript.Rmd
fix error

After filtering, we are left with `r dim(y)[1]` genes. We can then apply a
clustering routine. As observed by looking at genes found differentially expressed, 
many genes share a similar gene expression pattern, but on different scale.

@@

```{r topScoreInCluster2, fig.height=6, fig.width=6, fig.cap=paste("Top scoring genes in Cluster",cluster_of_interest)}
# order them by their score in cluster
ord = order(scores_and_labels$scores[genes_in_cluster2,
                     cluster_of_interest])
cluster2Score = genes_in_cluster2[ord]
dataToPlot = rbind(assay(moanin_model[cluster2Score[1:4], ]),
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(moanin_model, data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

>>>>

After filtering, we are left with `r dim(de_moanin_model)[1]` genes. We can then apply a
clustering routine. As observed by looking at genes found differentially expressed, 
many genes share a similar gene expression pattern, but on different scale.

@@

```{r topScoreInCluster2, fig.height=6, fig.width=6, fig.cap=paste("Top scoring genes in Cluster",cluster_of_interest)}
# order them by their score in cluster
ord = order(scores_and_labels$scores[genes_in_cluster2,
                     cluster_of_interest])
cluster2Score = genes_in_cluster2[ord]
dataToPlot = rbind(as.matrix(assay(moanin_model[cluster2Score[1:4], ])),
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(moanin_model, data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```
